---
title: "Logistic Regression"
subtitle: "Part II"
author: "Statistical Inference II"
date: "April 3, 2018"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(install.load)
install_load('tidyverse')
install_load('titanic')
```

```{r}
train <-
  titanic_train %>%
  drop_na()

str(train)
```

**Fit a GLM predicting probability of someone surviving (`Survived`) Titanic based on the amount of money they paid for the `Fare`.**

```{r}
model <- glm(Survived ~ Fare, family = binomial, data = train)
sm <- summary(model)
sm
```

**What is the estimated probability that someone survived if they paid $7 for the `Fare`?**

```{r}
exp(model$coefficients[[1]] + model$coefficients[[2]]*7)
```

**What is the estimated probability that someone survived if they paid $8 for the `Fare`?**

```{r}
exp(model$coefficients[[1]] + model$coefficients[[2]]*8)
```

**What is the estimated probability that someone survived if they paid $9 for the `Fare`?**

```{r}
exp(model$coefficients[[1]] + model$coefficients[[2]]*9)
```

**Interpret the estimated coefficients.**



**How does R calculate significance for the coefficients?**

```{r}
beta0 <- 1
beta1 <- 1
beta0.se <- 1
beta1.se <- 1

beta0.z <- 1
beta1.z <- 1

beta0.z <- 1
beta1.z <- 1
```


**What hypotheses are tested with the Wald-test?**


**How does R calculate confidence intervals for coefficients? **

**Interpret the following graph**

```{r}
ggplot(train,aes(x=Fare,y=Survived))+
  geom_point()+
  geom_smooth(data=train,method = "glm", 
    method.args = list(family = "binomial"), 
    se = FALSE)
```

**Add `Age` as a predictor. Does the model fit improve?**

```{r}
model.age <- glm(Survived ~ Fare + Age, family = binomial, data = train)
```

**Make a residual plot. Comment on the trend.**

```{r}
plot(model.age)
```
